Hector Permafrost

### 2018-12-18 README.Rmd
Set up drake. Add Schaefer 2011 CO2 emissions

>>>>

## Data description

- `analysis/data/raw_data/schaefer_teb_rpc_(min/max/mean).csv` -- Raw, digitized versions of Figure 5c (Ensemble mean and uncertainty of permafrost C respiration) in [@schaefer_2011_amount]. Original figure is `analysis/data/raw_data/schaefer_teb_timeseries.gif`. These results were digitized using WebPlotDigitizer (https://apps.automeris.io/wpd/), and interpolated to annual resolution (using R `stats::spline` function).
    - [@schaefer_2011_amount] assume only CO2 emissions. So we add this as an extra anthropogenic CO2 flux.

### 2018-12-18 analysis/paper/paper.Rmd
Set up drake. Add Schaefer 2011 CO2 emissions

Digitized scenarios from [@schaefer_2011_amount].

>>>>

For all scenarios, we added the emission as a combination of fossil fuel CO2 emissions (`ffi_emissions` column in Hector) and methane emissions (`CH4_emissions` column in Hector).
Where these were explicitly separated, we added them accordingly.
Where they were presented only in terms of C, we did ???

Digitized scenarios from [@schaefer_2011_amount].
SiBCASA model predictions of CO2 emissions (permafrost respiration; $R_{pc}$; note -- no methane!) through 2300.
These results were digitized using WebPlotDigitizer (https://apps.automeris.io/wpd/), and interpolated to annual resolution (using R `stats::spline` function).

Digitized scenarios from [@hope_2015_economic].
CO2 and CH4 emissions from SiBCASA model.

[@schuur_2009_effect] -- Estimate 0.8 - 1.1 Pg C yr-1.
